Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-28 WSSSPE3/report/wg_main_software_credit.tex
Fixed URL in SC main section

A number of groups external to WSSSPE (although with some overlapping members) are also focused on aspects of software credit, including the FORCE11 Software Citation Working Group (see plans for coordination below).
In addition, a Software Credit workshop\footnote{London Software Credit workshop: \url{www.software.ac.uk/software-credit}} convened in London on October 19, following the conclusion of WSSSPE3.
See \S\ref{sec:appendix_SW_credit} for more detailed discussion of related activities.

>>>>

A number of groups external to WSSSPE (although with some overlapping members) are also focused on aspects of software credit, including the FORCE11 Software Citation Working Group (see plans for coordination below).
In addition, a Software Credit workshop\footnote{London Software Credit workshop: \url{http://www.software.ac.uk/software-credit}} convened in London on October 19, following the conclusion of WSSSPE3.
See \S\ref{sec:appendix_SW_credit} for more detailed discussion of related activities.
